### 2020-03-05 Common/structure/info.tex
Julien and Johan: keywords

\subject{Computer Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{Prostate cancer classification, Convolutional Neural Networks (CNN), Transfer learning, PROSTATEx, Machine learning, Artificial intelligence} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.unifr.ch}{University of Fribourg}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{https://www3.unifr.ch/inf/fr/}{Department of Informatics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{https://www3.unifr.ch/inf/en/exascale-infolab.html}{eXascale Infolab}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{https://www3.unifr.ch/scimed/fr/}{Faculty of Science and Medicine}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

>>>>

\subject{Computer Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{Prostate cancer classification, Convolutional Neural Network (CNN), Transfer learning, PROSTATEx, Machine Learning (ML), Deep Learning (DL), Artificial Intelligence (AI)} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.unifr.ch}{University of Fribourg}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{https://www3.unifr.ch/inf/fr/}{Department of Informatics}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{https://www3.unifr.ch/inf/en/exascale-infolab.html}{eXascale Infolab}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{https://www3.unifr.ch/scimed/fr/}{Faculty of Science and Medicine}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
